---
title: "Paper Replication - Simulation"
author: "Your Name"
date: today
format:
  html:
    toc: true
    toc-float: true
    theme: united
    highlight-style: tango
---

We try to replicate the paper Miller, Nathan H., and Matthew C. Weinberg. "Understanding the Price Effects of the MillerCoors Joint Venture." Econometrica 85, no. 6 (2017): 1763–91. https://doi.org/10.3982/ECTA13333.

# Load Packages

```{r}
library(ggplot2)
library(magrittr)
devtools::load_all()
library(foreach)
library(doParallel)
registerDoParallel()
set.seed(1)
```

# Dimension
We first set up the following dimension for simulation. There are $R$ regions and $T = T_{pre} + T_{post}$ periods, where $T_{pre}$ is the number periods before the merger and $T_{post}$ is number the periods after the merger. Combination of region $r$ and period $t$ forms a market. Each market has $N$ consumers and $J$ products. Each product contains $1 + K_x$ dimensions of observed product characteristics, where the first dimension is an intercept. Also, each product contains $K_w$ dimensions of cost factors.

```{r}
constant <-
  set_constant()
constant
```


# Parameter
The conditional indirect utility that consumer $i$ receives from inside good $j$ in region $r$ and period $t$ is
$$
u_{ijrt} = x_j \beta_i^* + \alpha_i^* p_{jrt} + \sigma_j^D + \tau_t^D + \xi_{jrt} + \zeta_{igrt} + (1 - \rho) \varepsilon_{ijrt},
$$

where $[\alpha_i^*, \beta_i^*] = [\alpha, \beta]' + \Pi D_i$. Here the parameters of interest are $\alpha$, $\beta$, $\Pi$ and $\rho$.

From the marginal cost specification, we have
$$
mc_{jrt} = w_{jrt} \gamma + \sigma_j^S + \tau_t^S + \mu_r^S + \eta_{jrt}.
$$

Here the parameters of interest is $\gamma$. We take the first dimension of the cost factor to be the indicator for product from firm 2 or firm 3 post-merger (i.e. MillerCoors).

Also, in the post-merger ownership matrix
$$ 
\Omega_{t_2^*} = 
\begin{bmatrix}
1      & \kappa & \kappa & 0 \\
\kappa & 1      & 1      & 0 \\
\kappa & 1      & 1      & 0 \\
0      & 0      & 0      & 1
\end{bmatrix}.
$$

The parameter of interest here is $\kappa$.

```{r}
parameter <- 
  set_parameter(constant)
parameter
``` 

# Exogenous Variables
We proceed to draw exogenous variables. Demand-side exogenous variables include observed product characteristics $x_j$, fixed effect $\sigma_j^D$ and $\tau_t^D$. Supply-side exogenous variables include cost factors $w_{jrt}$, fixed effect $\sigma_j^S$, $\tau_t^S$ and $\mu_r^S$. Also, we have the demographic heterogeneity $D_i$, which is drawn at market level $(r, t)$. We store the observed product characteristics $x_j$ in the dataframe $X$, market-product charateristics, including cost factors and all fixed effect in $M$ and demographic heterogeneity in $D$. We also initialize a column for price $p$ in dataframe $M$ for later usage.


```{r}
X <-
  set_product_characteristics(
    constant = constant
    )

M <- 
  set_market_product(
    constant = constant
  )

D <- 
  set_demographic(
    constant = constant
)

exogenous <- 
  set_exogenous(constant)

exogenous
``` 

# Shock
We proceed to draw shocks. They are $\xi$ in the demand side and $\eta$ in the cost side.

```{r}
shock <- 
  set_shock(constant)

shock
``` 

# Endogenous Variables
There are two key endogenous variables in this model. The first one is the market share for each product $j$ in each market $(r, t)$. To obtain it, we first compute the following market-level mean indirect utility for product $j$,

$$
\delta_{jrt} = x_j \beta + \alpha p_{jrt} + \sigma_j^D + \tau_j^D + \xi_{jrt}.
$$

```{r}
delta <- 
  compute_delta(
    M = exogenous$M,
    X = exogenous$X,
    shock = shock,
    parameter = parameter
  )
delta
``` 

We also compute the individual level deviation from the market-level mean indirect utility,
$$
\mu_{ijrt} = [p_{jrt}, x_j]' * \Pi D_i
$$

```{r}
mu <- 
  compute_mu(
    M = exogenous$M,
    X = exogenous$X,
    D = exogenous$D,
    parameter = parameter
  )
mu
``` 

Since the heterogeneity is at market level, we expect to see identical deviation for distinct individuals in the same market.

We can then compute the mean indirect utility for each consumer $i$ in each market $(r, t)$ for each product $j$
```{r}
u_df <- 
  compute_indirect_utility(
    delta = delta,
    mu = mu
  )
u_df
``` 

From this we obtain the individual optimal choice probability by the following equation
$$
s_{ijrt} = \frac{exp((\delta_{jrt} + \mu_{ijrt})/(1 - \rho))}{exp(I_{igrt}/(1 - \rho))} \frac{exp(I_{igrt})}{exp(I_{irt})}.
$$,
where $I_{igrt}$ is the inclusive values for group $g$ goods,
$$
I_{igrt} = \begin{cases} 0, & \quad \text{if } g = 0,\\
(1 - \rho) log \sum_{j = 1}^{J_{rt}} exp((\delta_jrt + \mu_{ijrt}) / (1 - \rho)), & \quad \text{if } g = 1.
\end{cases}
$$

```{r}
u_df <- 
  classify_group(u_df)

u_df <-
  adjust_utility(
    u_df = u_df,
    rho = parameter$rho
    )

u_df <-
  compute_group_inclusive_value(
    u_df = u_df,
    rho = parameter$rho
  )

u_df <-
  compute_market_inclusive_value(
    u_df = u_df
    )

u_df <- 
  compute_share_df(
    u_df = u_df,
    rho = parameter$rho
  )

u_df
``` 

The market share of product $j$ in market $(r, t)$ is the mean of the individual optimal choice probability,
$$
s_{jrt} = \frac{1}{N_{rt}} \sum_{i = 1}^{N_{rt}} s_{ijrt}.
$$

```{r}
share_df <-
  compute_market_share_df(
    u_df = u_df
  )
share_df
``` 

The second endogenous variable is price from firm. The optimal pricing condition is given by 
$$
p_t = mc_t - \left[ \Omega_t(\kappa) \circ \left( \frac{\partial s_t(p_t; \theta^D)}{\partial p_t} \right)^T \right]^{-1} s_t(p_t; \theta^D).
$$

We first setup the ownership matrix $\Omega$
```{r}
omega <- 
  set_ownership(
    M = exogenous$M,
    T_pre = constant$T_pre,
    kappa = parameter$kappa
  )
omega[[1]][[2]]
omega[[5]][[14]]
``` 

We first obtain the marginal cost,
```{r}
cost <-
  compute_marginal_cost(
    M = exogenous$M,
    shock = shock,
    parameter = parameter
  )

cost$mc %>% head()
``` 

we also obtain the derivative,
```{r}
jacobian <-
  compute_jacobian_all(
    u_df = u_df,
    D = exogenous$D,
    constant = constant,
    parameter = parameter
  )

jacobian[[1]][[1]]
jacobian[[5]][[13]]
``` 

The function update_price first compute the marginal cost, then, base on the price given to the function, it computes the share, the derivatives of the shares with respect to price and the new optimal price.
```{r}
p <- cost[cost$j>0, "p"]
logp <- log(rep(1, dim(p)[1]))

p_new <- 
  update_price(
    logp = logp,
    M = exogenous$M,
    X = exogenous$X,
    D = exogenous$D,
    parameter = parameter,
    constant = constant,
    shock = shock,
    omega = omega
  )
p_new %>% head()
``` 


# Equilibrium
The equilibrium condition is given by a vector of market share $s^*$ and a vector of price $p^*$ where both are optimally computed through the aforementioned ways. Hence, we repeat the step of updating price until a stable price $p^*$.

```{r}
distance <- 10000
lambda = 1e-6
while (distance > lambda) {
  p_old <- p_new
  p_new <- 
    update_price(
      logp = log(p_old), 
      M = exogenous$M,
      X = exogenous$X,
      D = exogenous$D,
      parameter = parameter,
      constant = constant,
      shock = shock,
      omega = omega
    )
  distance <- max(abs(p_new - p_old))
  print(distance)
}
p_equilibrium <- p_new
p_equilibrium %>% head()
```

# Summarize variables
```{r}
M <- exogenous$M %>%
  dplyr::arrange(r, t, j)  # ensure proper ordering if needed

# Update prices for inside goods only
M[M$j > 0, "p"] <- p_equilibrium

delta <- compute_delta(
  M = M,
  X = exogenous$X,
  shock = shock,
  parameter = parameter
)

mu <- compute_mu(
  M = M,
  X = exogenous$X,
  D = exogenous$D,
  parameter = parameter
)

u_df <- compute_indirect_utility(
  delta = delta,
  mu = mu
)

u_df <- adjust_utility(
  u_df = u_df,
  rho = parameter$rho
)

u_df <- compute_group_inclusive_value(
  u_df = u_df,
  rho = parameter$rho
)

u_df <- compute_market_inclusive_value(
  u_df = u_df
)

u_df <- compute_share_df(
  u_df = u_df,
  rho = parameter$rho
)

s_df <- compute_market_share_df(
  u_df = u_df
)

summary_df <- 
  M %>%
  dplyr::filter(j > 0) %>%
  dplyr::select(j, r, t, p) %>%
  dplyr::left_join(
    s_df, 
    by = c("j", "r", "t")
  ) %>%
  dplyr::arrange(r, t, j)

summary_df <- summary_df %>%
  dplyr::mutate(
    merger_status = dplyr::if_else(
      t <= constant$T_pre, 
      "pre", 
      "post"
    )
  )

summary_table <- 
  summary_df %>%
  dplyr::mutate(
    merger_status = dplyr::if_else(
      t <= constant$T_pre,
      "pre",
      "post"
    )
  ) %>%
  dplyr::group_by(j, merger_status) %>%
  dplyr::summarise(
    mean_price = mean(p, na.rm = TRUE),
    sd_price   = sd(p, na.rm = TRUE),
    mean_share = mean(s, na.rm = TRUE),
    sd_share   = sd(s, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::arrange(j, merger_status)
summary_table
```
